---
title: "Solo Project"
---

# 5. Solo Project

## Introduction

Ice hockey is Canada’s national winter sport, but not every province fields the same number of NHL franchises.  
In this short project, I will map Canadian provinces by how many NHL teams they host and reflect on regional concentrations of top‑tier hockey markets.

```{r}
# Here I load required packages
library(sf)
library(dplyr)
library(ggplot2)
library(rnaturalearth)
library(rnaturalearthdata)
```


```{r}
# 1. Here I get Canada's provinces as an sf object
canada <- ne_states(country = "Canada", returnclass = "sf")

# 2. Here I compile number of NHL teams per province
nhl_counts <- tibble::tibble(
  name_en   = c("British Columbia", "Alberta", "Ontario", "Quebec", "Manitoba"),
  nhl_teams = c(1,                 2,         2,         1,        1)
)

# 3. Here I Left‑join and replace NA with 0 for provinces without NHL teams
canada_teams <- canada %>%
  left_join(nhl_counts, by = "name_en") %>%
  mutate(nhl_teams = tidyr::replace_na(nhl_teams, 0))

```

```{r}
# 4. Now onto building my choropleth map: 
ggplot(canada_teams) +
  geom_sf(aes(fill = nhl_teams), color = "white", size = 0.2) +
  scale_fill_viridis_c(
    option = "plasma", direction = -1,
    breaks = 0:2
  ) +
  labs(
    title    = "NHL Franchises by Canadian Province",
    subtitle = "Count of teams in each province (2025)",
    fill     = "NHL Teams",
    caption  = "Data: NHL official site; geography: Natural Earth"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.major = element_line(color = "gray80"),
    plot.title       = element_text(face = "bold", size = 20),
    plot.subtitle    = element_text(size = 16)
  )

```
Summary : British Columbia, Alberta, Ontario, Quebec, and Manitoba are the only five provinces to host NHL franchises.
The two biggest population centres, Toronto (Ontario) and Montreal (Quebec) each have a team, while Alberta’s two, Calgary and Edmonton, reflect the province’s strong hockey culture despite a smaller population.
Manitoba’s Winnipeg Jets carry a storied history of community revival, and British Columbia’s solitary team in Vancouver highlights the Pacific coast’s passion for the sport.
All other provinces (and territories) lack NHL presence, underscoring how market size and historical investment shape the geography of Canada’s top‑tier hockey.




